### 2020-06-21 magic_paper.tex

Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with $L \in \cal{B}(\cal{H})$, ensuring that the state is positive as well as Wigner-positive.

@@

    Expressed explicitly,
    \begin{equation}
		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
\end{definition}
\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.

@@

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
\begin{proposition}\label{thm:lccont}
	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
	I think this clears up the narrative quite a bit? - Should we keep and prove this result?}
\end{proposition}
The proof of this important result is in \nick{the appendix}.
The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
For simplicity, we restrict analysis to $\sigma$-fragments, where $\sigma$ is full-rank.

Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
As a consequence, checking whether a state conversion $\rho \longrightarrow \tau$ is possible as per~\cref{thm:dmajor}, reduces to the condition $\lc{\rho}{\sigma}(x) \leq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.

It can further be seen that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ \nick{CITE}, defined as the sum of the negative components in $\W{\rho}$.
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
	\begin{equation}
		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d^2$.

	Suppose that $\W{\rho}$ has at least one negative component.
	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
	\begin{align}
		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
		= \lc{\rho}{\sigma}(x_k)
		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
		= 1 + \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}} \\
		&= 1 + \sn{\rho}.
	\end{align}

We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity ($\rm{sn}$) further discussed in \nick{expand - move subsection on monotones (\cref{sec:mono}) in intro}.
Moreover, the area $\A_\sigma(\rho)$ of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}

@@

The most fundamental and commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.

@@

Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
\begin{equation}\label{eq:manabound}
    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
\end{equation}
A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
\end{equation}
If condition ${\rm{C}}_{\rm{maj}}$ is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.

In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.

    \ddd{[This is a bit too short]}\nick{I have added~\cref{lem:lcmax}}
\end{proof}

@@

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}.
\end{equation}
\ddd{[We can probably put upper and lower bounds on this value fairly readily. E.g. using known sum rules.]}

@@

\subsection{Magic in unital fragments}\label{sec:thermal}

>>>>

Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.

@@

    Expressed explicitly,
    \begin{equation}
		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
\end{definition}
\nick{Move the complicated last equation to appendix?}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.

@@

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
\begin{proposition}\label{thm:lccont}
	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
	I think this clears up the narrative quite a bit? - Should we keep and prove this result?} \ddd{[Is a nice result...hmm let's wait and see. It might distract from the main message.]}
\end{proposition}
The proof of this important result is in \nick{the appendix}.
The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
For simplicity, we restrict analysis to $\sigma$-fragments, where $\sigma$ is full-rank.

Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
As a consequence, checking whether a state conversion $\rho \longrightarrow \tau$ is possible as per~\cref{thm:dmajor}, reduces to the condition $\lc{\rho}{\sigma}(x) \leq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.

The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}

@@

The most fundamental and commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
	\sn{\rho} = \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}

@@

Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
\begin{equation}\label{eq:manabound}
    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
\end{equation}
A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
\end{equation}
If one of these consitions is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.

In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.

We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
	\begin{equation}
		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d^2$.

	Suppose that $\W{\rho}$ has at least one negative component.
	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
	\begin{align}
		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
		= \lc{\rho}{\sigma}(x_k)
		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
		= 1 + \sn{\rho}.
	\end{align}

\end{proof}
\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
We can therefore view mana as one of the features of the Lorenz curve, its maximum.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.
\end{proof}

@@

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right).
\end{equation}
%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]

@@

\subsection{Magic in unital fragments}\label{sec:unital}
